The Donald C. Backer Hydrogen Epoch of Reionization Array (HERA)

### 2014-07-02 hera-concept2013.tex
starting to clean up e.g. cite etc

\newcommand{\simgt}{\stackrel{>}{_{\sim}}}
\def\kperp{k_{\bot}}
\def\kpar{k_{\|}}
\def\k{{\bf k}}
\def\sky{{\theta}}
\def\HI{{H{\small I }}}
\def\HII{{H{\small II }}}
\def\xHI{{x_{\rm\HI}}}
\begin{document}

@@

@@

We have achieved a
pivotal new understanding of how instrumental characteristics give rise to the
wedge of emission shown in Figure \ref{fig:twoFGViews}.  Furthermore, we have
measurements that prove the efficacy, to the sensitivity limits of current
instruments, of projecting out foreground-dominated wavemodes within the
wedge.  The HI cosmology community is now in a position to define
the top-level instrument requirements that ensure foregrounds remain bounded
within the wedge, and to specify the sensitivity needed to obtain
high-significance detections of the 21~cm reionization power spectrum under the
conservative assumption that all foreground-dominated wavemodes within the
wedge must be projected out of our measurements.
As summarized in Table \ref{tab:signif} (see \Mycitealt{pober_et_al2014} for more details),
based on these assumptions, current instruments are likely to achieve,
at best, only marginal detections of power from reionization.

@@

%%		\Caption{-0.2in}{0.99}{-0.2in}{The PAPER element (provides a clean instrumental response as a function

@@

%%		\Caption{-0.2in}{0.99}{-0.2in}{A 14m dish designed around the feed dramatically improves sensitivity while

@@

%%\Caption{-0.2in}{0.99}{-0.2in}{PAPER and HERA elements}

@@

Since the time it takes radio emission to propagate between adjacent antennas 
represents a significant portion of this time budget, HERA elements must be placed close together.
Recent work characterizing foregrounds suggests that 
antenna separations of $8\lambda \approx 15$m are
well-behaved to current limits \Mycitep{pober_et_al2013,parsons_et_al2013}. This influences our
choice of a 14-m dish diameter,
which incurs 42 ns of signal delay between adjacent antennas.
The focal height (4.5 m) derives from the illumination pattern of the prime-focus
feed and the fact that reflections
between the feed and the element
%caused by imperfect impedance matching between the feed electronics and free space, 
can introduce additional signal delay. 
%With a splash cone underneath the feed to scatter reflections, we assume -20 dB
%attenuation per reflection, so that after three traversals (13.5 m; 41 ns), reflections from
%foreground emission are below the expected level of the 21~cm reionization signal.
Additional measures, such as a splash cone underneath the feed, screens that isolate feeds from one another, and 
non-metallic cabling and poles for supporting the feeds, are all aimed at minimizing
the potential for additional sources of signal reflections.
The total signal delay associated with the HERA dish design is estimated at 83 ns, leaving
headroom for reflections arising in the analog signal path.

@@

For HERA-127 and HERA-331, elements are arranged in a compact hexagonal grid.
This configuration minimizes antenna separation, which is critical for meeting
the science requirements for foreground isolation, and 
produces a highly redundant sampling of the $uv$ plane.  As described in
\S\ref{sec:Lessons}, redundant configurations have been employed by PAPER to
boost sensitivity \Mycitep{parsons_et_al2012a}, with the added benefit that they
greatly facilitate fast and accurate calibration
\Mycitep{liu_et_al2010,parsons_et_al2013}.  Placing HERA elements in a
grid allows certain construction components to be re-used between antennas,
reducing cost and improving the accuracy of element placement.  HERA-331 
is a build-out of HERA-127 from the eastern edge.

@@

HERA's analog signal path inherits directly from PAPER.
In keeping with a philosophy of
incremental change,
HERA-127 reuses the tested and commissioned feed, LNA, cables, and post-amplifier gain modules
(Fig. \ref{fig:components}, left and center) that are currently being
used to good effect in PAPER-128 \Mycitep{parsons_et_al2010}.  Existing PAPER feeds are attached to new
reflector screens that are suspended over the elements, but otherwise remain unmodified.
A parallel development effort in NRAO aims to improve the feed response below
100 MHz 
and to improve the match between polarization beams in the feed-element system.  
Additional
minor modifications to the analog signal path include transitioning from a 75$\Omega$ to a
shorter 50$\Omega$ cabling system and replacing 100--200 MHz bandpass filters with 50--250 MHz equivalents.
This wider analog bandwidth is used in HERA analysis to improve the extrapolation of smooth foreground
emission over a broader range, and to explore HERA's capability as a Dark-Ages science instrument.
After a Critical Design Review, the results of these development efforts are incorporated in
the transition to the HERA-331 system.

@@

\begin{figure}[t]\centering
\includegraphics[width=6.5in]{plots/casper_boards.jpg}
\Caption{-0.3in}{0.99}{-0.15in}{\small
Five generations of CASPER technology (progressing left to right) have been used to rapidly
develop, test, and deploy digital instrumentation for radio astronomy.  This technology
allows the PAPER correlator to be 
easily upgraded for HERA, incorporating new technology
\Mycitep{parsons_et_al2006,parsons_et_al2008}.
}\label{fig:casper_boards}
\end{figure}

%HERA's digital system continues in the vein of PAPER's digital correlators.
Although correlators have historically been one of the most complex,
expensive, and risky aspects of developing a radio interferometer, this is no longer the case.
CASPER \Mycitep{parsons_et_al2006}
open-sourced the development of digital signal processing engines for astronomy and
now has world-wide participation,
with over 500 members at 73 institutions, and 
five generations of hardware (Fig. \ref{fig:casper_boards}). 
On a modest budget, PAPER has applied CASPER technology to develop and deploy new correlators
annually for five years running, each quadrupling the computational capacity of its predecessor.
Led at UC Berkeley's Radio Astronomy Lab (RAL),
HERA efforts continue this incremental development cycle, following a packet-switched
correlator architecture \Mycitep{parsons_et_al2008} that has been
extended in recent PAPER and LEDA deployments (Fig. \ref{fig:components}, right)
to leverage the computing strengths of both FPGAs and GPUs \citep{clark_et_al2011}.

@@

HERA's data management system is responsible for recording raw data from the
correlator, compressing that data in real-time, applying routine calibration
and analysis pipelines, and transferring data products to 
a high-performance computing cluster at UPenn.
UPenn leads the procurement
and deployment of three data storage systems:
\begin{itemize}[noitemsep,nolistsep]
\item a 1.5 PB system deployed in the KAPB for archiving all 1.2 PB of raw data and 60 TB of compressed data, 
\item 6 network attached storage (NAS) units plus 2 125 TB RAID array units that are used to ship compressed data products to the US, and
\item a permanent 250 TB system at UPenn associated with a computing cluster that
holds compressed data products and serves as the analysis engine for HERA collaborators.
\end{itemize}
\noindent
This effort leverages existing infrastructure at UPenn, with support
for the expansion of the data storage and for upgrading to a 30-node computing cluster.  This cluster supports the bulk of the analysis by HERA collaborators (see \S\ref{sec:analysis}) that requires access to the full set of HERA observations.

@@

The data compression scheme at the heart of the data management system
has been implemented for PAPER (\Mycitealt{parsons_et_al2013},
Appendix A), and is applied to HERA visibilities to reduce data volume by
a factor of $\sim$20 without impacting reionization science
capabilities.  This compression technique, which is based on delay/delay-rate
filtering \Mycitep{parsons_backer2009}, is applied uniformly to all visibilities
in the array, does not require (or produce) detailed calibration
information, and is minimally restrictive for how data are analyzed and calibrated afterward.
Data compression is run on the same GPU servers
that implement the correlator X-Engines (\S\ref{sec:digital}).  Since HERA only observes at night,
these processors would otherwise be unused.  UC Berkeley is responsible for porting
the existing data compression pipeline to target these servers.

@@

The U. of Washington team leads the development of HERA's Monitor and Control (M\&C) system,
which is a straightforward port of a similar system used on the MWA \Mycitep{tingay_et_al2013}.
This system is
responsible for tracking observing status, array startup and shutdown, and
monitoring all active HERA systems. In the process, the M\&C system builds a sizeable database of 
metadata that is crucial for verifying system functionality, identifying hardware failures, and feeding
calibration and contextual information into data analysis pipelines.

@@

{\bf Foreground Modeling}. The U. Washington team leads the adaptation
of a high dynamic-range imaging pipeline
based on the Fast Holographic Deconvolution (FHD; \Mycitealt{sullivan_et_al2012}).
for HERA.  The full-Stokes sky maps resulting from this pipeline
are used to directly subtract foregrounds
and as data products themselves.  UPenn leads
the characterization of the polarized sky and the
distribution of rotation measures.  Data from HERA, PAPER, and the MWA are used
to update source catalogs and a Global
Sky Model \Mycitep{deoliveira2008}. %providing reference sky models for both
%HERA and other low-frequency instruments. %The goal will be to generate a model
%suitable for direct subtraction of foregrounds.

@@

{\bf Power Spectra}. UC Berkeley leads early power spectrum measurements using the conservative
delay-spectrum approach used in PAPER.  %This
%visibility-based approach, when coupled with a foreground-avoidance strategy,
%is sufficient for an unambiguous early detection of the 21~cm
%power spectrum should results from current-generation experiments prove
%marginal (Fig. \ref{fig:eor_pspec} and Table \ref{tab:signif}).  
Development of
the power-spectrum pipeline will focus on incorporating
a fully covariant description of the foreground wedge
\Mycitep{liu_tegmark2011,dillon_et_al2013a}, as well as
exploring Bayesian techniques for power spectrum estimation, building on the considerable
progress already made on Gibbs-sampling imaging for interferometers \Mycitep{sutter_et_al2014}.
In addition to the statistical foreground mitigation techniques provided by optimal quadratic
power-spectrum estimation, U. Washington leads the application of 
foreground modeling for expanding the range of modes available for power spectrum analysis.
Techniques developed should be equally applicable
to measurements in both the reionization epoch and at higher redshifts.  MIT leads the application
of these tools for pre-reionization science.

@@

\begin{thebibliography}{}

\bibitem[AUTHOR(YEAR)]{LABEL}
REFERENCE 1

\bibitem[AUTHOR(YEAR)]{LABEL}
REFERENCE 2

...

\end{thebibliography}

@@

\begin{figure}[t]
    \centering
        \includegraphics[height=1.5in]{plots/new_antenna_closeup.jpg}
        \includegraphics[height=1.5in]{plots/Engineering/recv_node.png}
        \includegraphics[height=1.5in]{plots/Engineering/digital.png}
    \Caption{-0.1in}{0.99}{-0.1in}{\small
    Existing components re-used in the HERA design include:
    the PAPER dipole antenna (left), 
    receivers in a node module (center), and
    the 128-element correlator deployed in the Karoo (right).
}\label{fig:components}
\end{figure}

@@

%\bottomhline
%\end{tabular}
%\end{table}
\begin{table}[t]
\small
 \centering
 \begin{tabular}{c||r||r|r} 
%\begin{deluxetable}{c||r||r|r}
%\tabletypesize{\small}
%\tablecaption{\small
\hline
%\startdata
Instrument & Collecting Area (m$^2$) & Foreground avoidance & Foreground modeling \\
\hline
PAPER & 528 & 1.93 & 8.86 \\
MWA & 896 & 2.46 & 6.40 \\
LOFAR NL Core & 35,762 & 2.76 & 17.37 \\
\textbf{HERA-127} & \textbf{19,500} & \textbf{10.88} & \textbf{35.65} \\
\textbf{HERA-331} & \textbf{50,900} & \textbf{25.44} & \textbf{87.20} \\
SKA1 Low Core & 833,190 & 97.92 & 284.85 \\
%\enddata
\end{tabular}
\Caption{-0.1in}{0.99}{-0.1in}{Power spectrum signal-to-noise (``number of sigmas") at $z=9.5$ for various instruments, adapted from \Mycitet{pober_et_al2014}.  By leveraging a filled, redundant configuration of dishes with high collecting area, HERA-331 allows high-significance power spectrum measurements using current foreground avoidance techniques, with further enhancements possible with likely advances in foreground modeling.}
\label{tab:signif}
\end{table}

\begin{table}[t]
\small
\begin{center}
% \begin{deluxetable}{lcc}
% \tabletypesize{\small}
% \tablecaption{HERA-331 basic parameters.}
% \tablehead{\colhead{Parameter} & \colhead{Design} & \colhead{Performance at 150 MHz}}
%    \startdata
\begin{tabular}{l | c | c}
\hline
Parameter & Design & Performance\\
\hline
    Element diameter / FoV & 14 m & 9\arcdeg \\ 
    %Total collecting area & 54186 m$^2$ \\
    Min baseline length / largest scale & 14.6 m & 7.8\arcdeg \\
    Max core baseline length / synthesized beam & 306.6 m & 24\arcmin \\ 
    Max outrigger baseline length  & 1066.5 m & 9\arcmin \\
    Frequency / redshift range  & 50 - 250 MHz digitized \\
    & 70 - 230 MHz useable & 19.2 - 5.2 \\ 
    & 100 MHz correlated & \\
    Spectral channel width & 97.7 kHz & \\    
    System temperature / sensitivity & $100 + 120 (\nu/\rm{150~MHz})^{-2.55}$ K 
    & 50 $\mu \rm{Jy}~\rm{beam}^{-1}~\sqrt{\rm{hour}}$ \\
    \hline
%     At 150 MHz ($z=8.5$): & \\
%     ~{   }Naturally weighted synthesized beam FWHM & $24\arcmin$ \\
%     ~{   }Uniformly weighted synthesized beam FWHM & $9\arcmin$ \\
%     ~{   }Field of view FWHM & 9\arcdeg \\
%     ~{   }Point source RMS & 50 $\mu$Jy in 100 hrs \\
%  \enddata
%    \hline
 %\end{deluxetable}
\end{tabular}
\Caption{-0.1in}{0.99}{-0.4in}{HERA-331 basic parameters.  Design parameters are connected to the derived instrument performance at 150 MHz.}
\label{tab:BasicParameters}
\vspace{.2in}
%\end{deluxetable}
\end{center}
\end{table}

>>>>

\newcommand{\simgt}{\stackrel{>}{_{\sim}}}
\def\kperp{k_{\bot}}
\def\kpar{k_{\|}}
\def\k{{\bf k}}
\def\sky{{\theta}}
\def\HI{{H{\small I }}}
\def\HII{{H{\small II }}}
\def\xHI{{x_{\rm\HI}}}
\def\arcdeg{{$^o$}}
\def\arcmin{{$''$}}
\begin{document}

@@

% Intro
% Background
% Scientific Motivation
% Specifications
% System Overview
% Data Processing
% Site?
% Conclusion

@@

We have achieved a
pivotal new understanding of how instrumental characteristics give rise to the
wedge of emission shown in Figure \ref{fig:twoFGViews}.  Furthermore, we have
measurements that prove the efficacy, to the sensitivity limits of current
instruments, of projecting out foreground-dominated wavemodes within the
wedge.  The HI cosmology community is now in a position to define
the top-level instrument requirements that ensure foregrounds remain bounded
within the wedge, and to specify the sensitivity needed to obtain
high-significance detections of the 21~cm reionization power spectrum under the
conservative assumption that all foreground-dominated wavemodes within the
wedge must be projected out of our measurements.
As summarized in Table \ref{tab:signif} (see \citealt{pober_et_al2014} for more details),
based on these assumptions, current instruments are likely to achieve,
at best, only marginal detections of power from reionization.

@@

%%		\caption{-0.2in}{0.99}{-0.2in}{The PAPER element (provides a clean instrumental response as a function

@@

%%		\caption{-0.2in}{0.99}{-0.2in}{A 14m dish designed around the feed dramatically improves sensitivity while

@@

%%\caption{-0.2in}{0.99}{-0.2in}{PAPER and HERA elements}

@@

Since the time it takes radio emission to propagate between adjacent antennas 
represents a significant portion of this time budget, HERA elements must be placed close together.
Recent work characterizing foregrounds suggests that 
antenna separations of $8\lambda \approx 15$m are
well-behaved to current limits \citep{pober_et_al2013,parsons_et_al2013}. This influences our
choice of a 14-m dish diameter,
which incurs 42 ns of signal delay between adjacent antennas.
The focal height (4.5 m) derives from the illumination pattern of the prime-focus
feed and the fact that reflections
between the feed and the element
%caused by imperfect impedance matching between the feed electronics and free space, 
can introduce additional signal delay. 
%With a splash cone underneath the feed to scatter reflections, we assume -20 dB
%attenuation per reflection, so that after three traversals (13.5 m; 41 ns), reflections from
%foreground emission are below the expected level of the 21~cm reionization signal.
Additional measures, such as a splash cone underneath the feed, screens that isolate feeds from one another, and 
non-metallic cabling and poles for supporting the feeds, are all aimed at minimizing
the potential for additional sources of signal reflections.
The total signal delay associated with the HERA dish design is estimated at 83 ns, leaving
headroom for reflections arising in the analog signal path.

@@

For HERA-127 and HERA-331, elements are arranged in a compact hexagonal grid.
This configuration minimizes antenna separation, which is critical for meeting
the science requirements for foreground isolation, and 
produces a highly redundant sampling of the $uv$ plane.  As described in
\S\ref{sec:Lessons}, redundant configurations have been employed by PAPER to
boost sensitivity \citep{parsons_et_al2012a}, with the added benefit that they
greatly facilitate fast and accurate calibration
\citep{liu_et_al2010,parsons_et_al2013}.  Placing HERA elements in a
grid allows certain construction components to be re-used between antennas,
reducing cost and improving the accuracy of element placement.  HERA-331 
is a build-out of HERA-127 from the eastern edge.

@@

HERA's analog signal path inherits directly from PAPER.
In keeping with a philosophy of
incremental change,
HERA-127 reuses the tested and commissioned feed, LNA, cables, and post-amplifier gain modules
(Fig. \ref{fig:components}, left and center) that are currently being
used to good effect in PAPER-128 \citep{parsons_et_al2010}.  Existing PAPER feeds are attached to new
reflector screens that are suspended over the elements, but otherwise remain unmodified.
A parallel development effort in NRAO aims to improve the feed response below
100 MHz 
and to improve the match between polarization beams in the feed-element system.  
Additional
minor modifications to the analog signal path include transitioning from a 75$\Omega$ to a
shorter 50$\Omega$ cabling system and replacing 100--200 MHz bandpass filters with 50--250 MHz equivalents.
This wider analog bandwidth is used in HERA analysis to improve the extrapolation of smooth foreground
emission over a broader range, and to explore HERA's capability as a Dark-Ages science instrument.
After a Critical Design Review, the results of these development efforts are incorporated in
the transition to the HERA-331 system.

@@

\begin{figure}[t]\centering
\includegraphics[width=6.5in]{plots/casper_boards.jpg}
\caption{-0.3in}{0.99}{-0.15in}{\small
Five generations of CASPER technology (progressing left to right) have been used to rapidly
develop, test, and deploy digital instrumentation for radio astronomy.  This technology
allows the PAPER correlator to be 
easily upgraded for HERA, incorporating new technology
\citep{parsons_et_al2006,parsons_et_al2008}.
}\label{fig:casper_boards}
\end{figure}

%HERA's digital system continues in the vein of PAPER's digital correlators.
Although correlators have historically been one of the most complex,
expensive, and risky aspects of developing a radio interferometer, this is no longer the case.
CASPER \citep{parsons_et_al2006}
open-sourced the development of digital signal processing engines for astronomy and
now has world-wide participation,
with over 500 members at 73 institutions, and 
five generations of hardware (Fig. \ref{fig:casper_boards}). 
On a modest budget, PAPER has applied CASPER technology to develop and deploy new correlators
annually for five years running, each quadrupling the computational capacity of its predecessor.
Led at UC Berkeley's Radio Astronomy Lab (RAL),
HERA efforts continue this incremental development cycle, following a packet-switched
correlator architecture \citep{parsons_et_al2008} that has been
extended in recent PAPER and LEDA deployments (Fig. \ref{fig:components}, right)
to leverage the computing strengths of both FPGAs and GPUs \citep{clark_et_al2011}.

@@

HERA's data management system is responsible for recording raw data from the
correlator, compressing that data in real-time, applying routine calibration
and analysis pipelines, and transferring data products to 
a high-performance computing cluster at UPenn.
UPenn leads the procurement
and deployment of three data storage systems:
\begin{itemize}%[noitemsep,nolistsep]
\item a 1.5 PB system deployed in the KAPB for archiving all 1.2 PB of raw data and 60 TB of compressed data, 
\item 6 network attached storage (NAS) units plus 2 125 TB RAID array units that are used to ship compressed data products to the US, and
\item a permanent 250 TB system at UPenn associated with a computing cluster that
holds compressed data products and serves as the analysis engine for HERA collaborators.
\end{itemize}
\noindent
This effort leverages existing infrastructure at UPenn, with support
for the expansion of the data storage and for upgrading to a 30-node computing cluster.  This cluster supports the bulk of the analysis by HERA collaborators (see \S\ref{sec:analysis}) that requires access to the full set of HERA observations.

@@

The data compression scheme at the heart of the data management system
has been implemented for PAPER (\citealt{parsons_et_al2013},
Appendix A), and is applied to HERA visibilities to reduce data volume by
a factor of $\sim$20 without impacting reionization science
capabilities.  This compression technique, which is based on delay/delay-rate
filtering \citep{parsons_backer2009}, is applied uniformly to all visibilities
in the array, does not require (or produce) detailed calibration
information, and is minimally restrictive for how data are analyzed and calibrated afterward.
Data compression is run on the same GPU servers
that implement the correlator X-Engines (\S\ref{sec:digital}).  Since HERA only observes at night,
these processors would otherwise be unused.  UC Berkeley is responsible for porting
the existing data compression pipeline to target these servers.

@@

The U. of Washington team leads the development of HERA's Monitor and Control (M\&C) system,
which is a straightforward port of a similar system used on the MWA \citep{tingay_et_al2013}.
This system is
responsible for tracking observing status, array startup and shutdown, and
monitoring all active HERA systems. In the process, the M\&C system builds a sizeable database of 
metadata that is crucial for verifying system functionality, identifying hardware failures, and feeding
calibration and contextual information into data analysis pipelines.

@@

{\bf Foreground Modeling}. The U. Washington team leads the adaptation
of a high dynamic-range imaging pipeline
based on the Fast Holographic Deconvolution (FHD; \citealt{sullivan_et_al2012}).
for HERA.  The full-Stokes sky maps resulting from this pipeline
are used to directly subtract foregrounds
and as data products themselves.  UPenn leads
the characterization of the polarized sky and the
distribution of rotation measures.  Data from HERA, PAPER, and the MWA are used
to update source catalogs and a Global
Sky Model \citep{deoliveira2008}. %providing reference sky models for both
%HERA and other low-frequency instruments. %The goal will be to generate a model
%suitable for direct subtraction of foregrounds.

@@

{\bf Power Spectra}. UC Berkeley leads early power spectrum measurements using the conservative
delay-spectrum approach used in PAPER.  %This
%visibility-based approach, when coupled with a foreground-avoidance strategy,
%is sufficient for an unambiguous early detection of the 21~cm
%power spectrum should results from current-generation experiments prove
%marginal (Fig. \ref{fig:eor_pspec} and Table \ref{tab:signif}).  
Development of
the power-spectrum pipeline will focus on incorporating
a fully covariant description of the foreground wedge
\citep{liu_tegmark2011,dillon_et_al2013a}, as well as
exploring Bayesian techniques for power spectrum estimation, building on the considerable
progress already made on Gibbs-sampling imaging for interferometers \citep{sutter_et_al2014}.
In addition to the statistical foreground mitigation techniques provided by optimal quadratic
power-spectrum estimation, U. Washington leads the application of 
foreground modeling for expanding the range of modes available for power spectrum analysis.
Techniques developed should be equally applicable
to measurements in both the reionization epoch and at higher redshifts.  MIT leads the application
of these tools for pre-reionization science.

@@

\bibliographystyle{copernicus}
\bibliography(biblio)

%\begin{thebibliography}{}
%
%\bibitem[AUTHOR(YEAR)]{LABEL}
%REFERENCE 1
%
%\bibitem[AUTHOR(YEAR)]{LABEL}
%REFERENCE 2
%
%...
%
%\end{thebibliography}

@@

\begin{figure}[t]
    \centering
        \includegraphics[height=1.5in]{plots/new_antenna_closeup.jpg}
        \includegraphics[height=1.5in]{plots/Engineering/recv_node.png}
        \includegraphics[height=1.5in]{plots/Engineering/digital.png}
    \caption{-0.1in}{0.99}{-0.1in}{\small
    Existing components re-used in the HERA design include:
    the PAPER dipole antenna (left), 
    receivers in a node module (center), and
    the 128-element correlator deployed in the Karoo (right).
}\label{fig:components}
\end{figure}

@@

%\bottomhline
%\end{tabular}
%\end{table}
\begin{table*}[t]
\small
 \centering
 \begin{tabular}{c||r||r|r} 
%\begin{deluxetable}{c||r||r|r}
%\tabletypesize{\small}
%\tablecaption{\small
\hline
%\startdata
Instrument & Collecting Area (m$^2$) & Foreground avoidance & Foreground modeling \\
\hline
PAPER & 528 & 1.93 & 8.86 \\
MWA & 896 & 2.46 & 6.40 \\
LOFAR NL Core & 35,762 & 2.76 & 17.37 \\
\textbf{HERA-127} & \textbf{19,500} & \textbf{10.88} & \textbf{35.65} \\
\textbf{HERA-331} & \textbf{50,900} & \textbf{25.44} & \textbf{87.20} \\
SKA1 Low Core & 833,190 & 97.92 & 284.85 \\
%\enddata
\end{tabular}
\caption{Power spectrum signal-to-noise (``number of sigmas") at $z=9.5$ for various instruments, adapted from \citet{pober_et_al2014}.  By leveraging a filled, redundant configuration of dishes with high collecting area, HERA-331 allows high-significance power spectrum measurements using current foreground avoidance techniques, with further enhancements possible with likely advances in foreground modeling.}
\label{tab:signif}
\end{table*}

Print this is some text in between.

\begin{table*}[t]
\small
%\begin{center}
% \begin{deluxetable}{lcc}
% \tabletypesize{\small}
% \tablecaption{HERA-331 basic parameters.}
% \tablehead{\colhead{Parameter} & \colhead{Design} & \colhead{Performance at 150 MHz}}
%    \startdata
\begin{tabular}{l | c | c} \hline
Parameter & Design & Performance\\  \hline
    Element diameter / FoV & 14 m & 9\arcdeg \\ 
    %Total collecting area & 54186 m$^2$ \\
    Min baseline length / largest scale & 14.6 m & 7.8\arcdeg \\
    Max core baseline length / synthesized beam & 306.6 m & 24\arcmin \\ 
    Max outrigger baseline length  & 1066.5 m & 9\arcmin \\
    Frequency / redshift range  & 50 - 250 MHz digitized \\
    & 70 - 230 MHz useable & 19.2 - 5.2 \\ 
    & 100 MHz correlated & \\
    Spectral channel width & 97.7 kHz & \\    
    System temperature / sensitivity & $100 + 120 (\nu/\rm{150~MHz})^{-2.55}$ K 
    & 50 $\mu \rm{Jy}~\rm{beam}^{-1}~\sqrt{\rm{hour}}$ \\
    \hline
%     At 150 MHz ($z=8.5$): & \\
%     ~{   }Naturally weighted synthesized beam FWHM & $24\arcmin$ \\
%     ~{   }Uniformly weighted synthesized beam FWHM & $9\arcmin$ \\
%     ~{   }Field of view FWHM & 9\arcdeg \\
%     ~{   }Point source RMS & 50 $\mu$Jy in 100 hrs \\
%  \enddata
%    \hline
 %\end{deluxetable}
\end{tabular}
\caption{HERA-331 basic parameters.  Design parameters are connected to the derived instrument performance at 150 MHz.}
\label{tab:BasicParameters}
\vspace{.2in}
%\end{deluxetable}
%\end{center}
\end{table*}
